Fictitious Play in Network Aggregative Games

### 2021-05-20 Documents/FP in NAGs/neurips_2020.tex
minor mods

  Fictitious Play requires that, at the current time, each agent considers the average state
  of their opponent in the past, and respond optimally (i.e. play a best response) to this state. In the case of an NA game, each agent considers their reference vector to be their
  opponent. As such, each agent $\mu$ must update their state according to the time-average of
  $\refmu$. To formalise this we write

@@

  Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
  Fictitious Play in continuous time, but with a slight adaptation for the NA game.
%
  \begin{definition}[Network Aggregative - Continuous Time Fictitious Play (NA-CTFP)]
    An NA-CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
    and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
    BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
  \end{definition}

@@

  \begin{remark}
    As an illustration, consider the NA game with two players, in which $\edgeset = \{(1, 2),
    (2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
    the off diagonal. We write the time-average of both agents' state as

    \begin{align}
      \alpha^\mu(t; x) = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
  %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
    \end{align}

    In this manner, the $\alpha^\mu(t; m)$ denotes the time average of the strategies played by
    agent $\mu$ up to time $t$ when the strategies are given by $\xmu(t)$. Note that we often reduce the notation to $\alpha^\mu(t)$. Then, fictitious play requires that the agents update their
    strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t) \in BR^2(\alpha^1(t))$. It can be
    seen, therefore, that the NA-CTFP is a natural extension of CTFP in the classical
    two-player setting \cite{}.
  \end{remark}

@@

  \begin{assumption}\label{ass::rowstochastic}
    The weighted adjacency matrix $\weightset$ is constant and \emph{row stochastic} meaning
    that the sum elements in each row of $\weightset$ is equal to one. This assumption is
    made to ensure that the analysis of NA games can be derived as a natural extension to the
    classical setting of two-player games. We can think of the row stochastic condition as the
    ability of each agent to prioritise the state information it receives from each of its
    neighbours. It is also a classical assumption made in the analysis of network games
    \cite{one of the network game papers} and can is straightforward to implement \cite{Eyad}.
  \end{assumption}

@@

  \begin{assumption}\label{ass::sameactions}
    The cardinality of each action set $|\actionset{\mu}|$ is equal for all agents. This is
    a classical assumption which is made in most game theoretic settings and includes, as a
    special case, the analysis of homogeneous agents \cite{}. However, it should be noted that,
    in \cite{Ewerhart}, CTFP was analysed without this requirement.  
  \end{assumption}

  \begin{assumption}\label{ass::zerosum}
    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu, \weightedsum)$ for any set
    of states $(x^\mu)_{\mu \in N^\mu}$. This is, perhaps, one of the stronger assumptions in
    our analysis, and is required for the fixed point analysis. However, in Section
    \ref{sec::CCEConvergence}, we perform a regret analysis that considers the long term
    behaviour of NA-CTFP without this assumption.
  \end{assumption}

>>>>

  Fictitious Play requires that, at the current time, each agent
  considers the average state of their opponent in the past, and
  respond optimally (i.e., play a best response) to this state. In the
  case of an NA game, each agent considers their reference vector to
  be their opponent. As such, each agent $\mu$ must update their state
  according to the time-average of $\refmu$. To formalise this we
  write

  \fb{What is $\avgref{\mu}$?}

@@

  Using this, we follow \cite{Ewerhart,Harris}
  %in the footsteps of Ewerhart \cite{} and Harris \cite{}
  to define
  Fictitious Play in continuous time, but adapted
  %with a slight adaptation for the
  to NA games.
  %
  \fb{is there any way we can make the following definition more intuitive?}
  \begin{definition}[NA-CTFP]
    A {\em network aggregative - continuous time fictitious play} is
    defined as a measurable map $m$ with components $m^\mu$ such that
    for all $\mu$ and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow
      \Delta_\mu$ satisfies $m^\mu(t) \in BR^\mu(\alpha_{\sigma}^\mu)$
      for almost all $t \geq 1$.
  \end{definition}

@@

  \begin{remark}
    As an illustration, consider the NA game with two players, in which $\edgeset = \{(1, 2),
    (2, 1)\}$ and $\weightset$ is a 2x2 matrix with zeros on its leading diagonal and ones on
    the off diagonal. We write the time-average of both agents' state as
%  
%    \begin{align}
 $     \alpha^\mu(t; x) = \frac{1}{t} \int_0^{\fb{t}} \xmu(t) \, dt$, for $\mu \in \{1, 2\}$.
  %   \alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
    %    \end{align}

   Hence, $\alpha^\mu(t; m)$ denotes the time average of the
   strategies played by agent $\mu$ up to time $t$ when the strategies
   are given by $\xmu(t)$. Note that we often reduce the notation to
   $\alpha^\mu(t)$. Then, fictitious play requires that the agents
   update their strategy as $x^1(t) \in BR^1(\alpha^2(t))$ and $x^2(t)
   \in BR^2(\alpha^1(t))$. It can be seen, therefore, that the NA-CTFP
   is a natural extension of CTFP in the classical two-player setting
   \cite{}.
  \end{remark}

  \fb{these remarks are very helpful.}

@@

  \begin{assumption}\label{ass::rowstochastic}
    The weighted adjacency matrix $\weightset$ is constant and
    \emph{row stochastic}, meaning that the sum elements in each row
    of $\weightset$ is equal to one. This assumption is made to ensure
    that the analysis of NA games can be derived as a natural
    extension to the classical setting of two-player games. We can
    think of the row stochastic condition as the ability of each agent
    to prioritise the state information it receives from each of its
    neighbours. It is also a classical assumption made in the analysis
    of network games \cite{one of the network game papers} and is
    straightforward to implement \cite{Eyad}.
  \end{assumption}

@@

  \begin{assumption}\label{ass::sameactions}
    The cardinality of each action set $|\actionset{\mu}|$ is equal
    for all agents. This is a classical assumption which is made in
    most game-theoretic settings and includes, as a special case, the
    analysis of homogeneous agents \cite{}. However, it should be
    noted that, in \cite{Ewerhart}, CTFP was analysed without this
    requirement.
  \end{assumption}

  \begin{assumption}\label{ass::zerosum}
    The NA game is zero-sum in the sense that $\sum_{\mu} u^\mu(\xmu,
    \weightedsum)$ for any set of states $(x^\mu)_{\mu \in
      N^\mu}$. This is, perhaps, one of the strongest assumptions in
    our analysis, and is required for the fixed point
    analysis \fb{repetition}. Nonetheless, in Section \ref{sec::CCEConvergence}, we
    perform a regret analysis that considers the long term behaviour
    of NA-CTFP without this assumption.
  \end{assumption}
